\TitleText

### 2020-06-09 presentation/1_introduction.tex
Update presentation

\I The design of new algorithms addressing these issues requires channel information to be known.

@@

\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we exploit to save for some measurements.
}

>>>>

\I The design of various algorithms requires channel information to be known.

@@

\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we might exploit to reduce complexity.
}

### 2020-06-09 presentation/2_setting.tex
Update presentation

\I Problem (a): How do we recover \m {\M {H}} with knowledge of \m {\M {Y}}?

\I Problem (b): How do we design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a linear equation
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Compressive Sensing}
{
\I In our case, we have to essentially invert an underdetermined system, and usually, that is not well defined.

\I Consider a simpler case: \m {\V {y} = \M {A} \V {x} + \V {z}}, where \m {\M {A} \in \MB {R} ^{N_m \D N_p}}, \m {\V {y} \in \MB {C} ^{N_m}}.

\I If \m {\V {y} = \M {A} \V {x}_1 = \M {A} \V {x}_2}
\Disp {
\NC \V {x}_1 - \V {x}_2 \in \Rm {null}\; \M {A} \NR
}
Then \m {\V {x}_1, \V {x}_2} cannot be recovered.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Restricted Isometry Property}
{
\I However, Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.

\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

@@

\I Verbally, \m {\m {P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Dantzig Selector for Sparse Vectors}
{
\I Let \m {\V {x}} be \m {S}-sparse.
If \m {\g_{\Ss {DS}} = \R {2 \log N_p}}, then
\Disp {
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}  \MC \VNm {\V {x}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {A}^\intercal \RB {\V {y} -\M {A} \V {x}'}} _\infty \leq \g_{\Ss {DS}} \NR
\stopcases \NR
}
with
\Disp {
\NC \VNm {\V {x} - \hat {\V {x}}} _2 ^2
\leq \NC 32 S \sigma^2 \log N_p \NR
}
For high probability.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Back to our problem: Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

>>>>

\I Problem (a): Recover \m {\M {H}} with knowledge of \m {\M {Y}}?

\I Problem (b): Design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a linear equation, where we have to essentially invert an underdetermined system:
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Terminology}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

@@

\I We may think \m {\m {P}} to be almost unitary up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Dantzig Selector for Sparse Vectors}
{
\I Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.

\I Let \m {\V {x}} be \m {S}-sparse.
If \m {\g_{\Ss {DS}} = \R {2 \log N_p}}, then
\Disp {
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}  \MC \VNm {\V {x}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {A}^\intercal \RB {\V {y} -\M {A} \V {x}'}} _\infty \leq \g_{\Ss {DS}} \NR
\stopcases \NR
}
with
\Disp {
\NC \VNm {\V {x} - \hat {\V {x}}} _2 ^2
\leq \NC 32 S \sigma^2 \log N_p \NR
}
For high probability.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Back to our problem: Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

### 2020-06-09 presentation/3_proof.tex
Update presentation

\Frame {Modifying the Original Proof}
{
\I \Emph{Q1}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?

\I \Emph {Q2}: DS works for \Emph {sparse} vectors, but as \m {\M {H}} is not sparse, does DS work?

\I \Emph{Q3}: DS requires the measurement matrix to have restricted isometry property, but under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, is it true for \m {\M {P}}?

\I \Emph{Q4}: Candès and Tao showed the Big-\m {\MC {O}} of error norm depends on (in our case) \m {N_H}, but does the algorithm work successfully for \Emph {high probability}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Real Valued Representation}
{
\I To save complexity, we represent a complex number by its real- and imarinary-parts.

\I For vectors, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a \NR
\NC b \NR
\stopTheMatrix \NR
}

\I For matrices, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a, \NC -b \NR
\NC b, \NC a \NR
\stopTheMatrix \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %

\Frame {Observations on Sparsity}
{
\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we still have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.

\I Establish that all four beamformers satisfy RIP, for high probability, thus \m {\m {P}} satisfies RIP too, for high probability.

\I We then establish a modified bound of error norm.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC S
= L \log N_H,
\Q \d_S
\leq \F {1} {8} \NR
}

@@

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I I argue in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?

\I Try to set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And let each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP...

\I for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error Norm of Dantzig Selector}
{
\I The following bound holds for high probability \m {p}:
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
}

\I where it hold for \m {p} that...
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability}
{
\I Denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q = 1-p
\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I If we provide the design values
\Disp {
\NC N_Y
\gtrsim \NC 4 \log N_H, \Q
N_R
\gtrsim 16 L \RB {\log N_H}^2 \NR
}

\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R} \NR
%
\NC q
\lesssim \NC 2 N_H ^{-1/3} \NR
}
}

>>>>

\Frame {Modifying the Original Proof (1/2)}
{
\I DS works for real matrices, but we generalize by representing a complex number by its real- and imarinary-parts.

\I DS works for sparse vectors, but \m {\M {H}} is not sparse.
We claim that \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Modifying the Original Proof (2/2)}
{
\I DS requires the measurement matrix (in our case) \m {P} to have restricted isometry property.
We shall design all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, so that for high probability, they satisfies RIP, thus \m {\m {P}} does too.

\I We know the Big-\m {\MC {O}} of error norm of DS depends on (in our case) \m {N_H}.
We consider these failure events above, and claim that the algorithm works for high probability.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC S
= L \log N_H,
\Q \d_S
\leq \F {1} {8} \NR
}

@@

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant

\I It is argued in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has too.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Bound of Error Norm (1/2)}
{
\I The following bound holds for probability \m {p}:
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
}
%
\I where for \m {p}, denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q = 1-p
\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I Then...
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Bound of Error Norm (2/2)}
{
\I For concreteness, set values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \NR
\NC N_R \gtrsim \NC 16 L \RB {\log N_H}^2 \NR
}
%
\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R} \NR
%
\NC q
\lesssim \NC 2 N_H ^{-1/3} \NR
}
}

### 2020-06-09 presentation/4_simulation.tex
Update presentation

\I Apply pseudoinverse (linear square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.

\I Assign corresponding components of \m {\Hat {\V {g}}_2} in \m {\Hat {\V {g}}}, and pad \m {0} otherwise.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I With some approximations, I suggest the following metric for spectral efficiency:
\I Denote \m {E := \Hat {H} - H}
\I Observe
\Disp {
\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj - \M {H} \M {H} ^\Adj} \V {x}
\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
}
\I Define the spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Theoretical Metric}
{
\I For the theoretical error norm,
\Disp {
\NC \log d_{\Rm {th}}
\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H \NR
}
\I Define the theoretical spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 d_{\Rm {th}} \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 20, 24}
\I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
\I Antennae number of digital stage \m {N_Y = \lfloor N_H/3 \rfloor}
\I Number of paths \m {L =3}
\I Analog beamformer quantization grid: \m {16}
\I How many noise standard deviation tried: \m {7}
\I Number of repetition of each data point: \m {12}
\I Solved by Python CVXPY
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS is slightly better than others when \m {\s \gg 1}

\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}

\I The smaller the noise, the smaller the error

\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error

\I We have exceedingly high complexity than OMP

\I The requirement that \m {N_H \gg N_Y} is demanding
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (1/2)}
{
\I In general, the complexity of convex optimization is hard to obtain.

\I However, there exist expressions for number of Newton steps in the course of optimization.
It is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.

\I Moreover, every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
This gives \m {\MC {O} \SB {N_H^6}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (2/2)}
{
\I On the other hand, it is pointed out that Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
Since DS and Lasso have similar form, we expect DS has similar complexity.

\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, so much smaller than DS.
}

>>>>

\I Apply pseudoinverse (least square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.

\I Assign corresponding components of \m {\Hat {\V {g}}_2} in \m {\Hat {\V {g}}}, and pad \m {0} otherwise.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I We call the following quantity \m {M} to be the efficiency, in view of approximate spectral efficiency:
\I Denote \m {E := \Hat {H} - H}.
Assume that
\Disp {
\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj \V {x} - \M {H} \M {H} ^\Adj \V {x}} _2
\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
}
\I Then define
\Disp {
\NC M
= \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Theoretical Prediction}
{
\I For the theoretical error norm,
\Disp {
\NC \log d_{\Rm {th}}
\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H \NR
}
\I Then we may well define the theoretical efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 d_{\Rm {th}} \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 12, 18, 24}
\I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
\I Antennae number of digital stage \m {N_Y = \lfloor N_H/3 \rfloor}
\I Number of paths \m {L =3}
\I Analog beamformer quantization grid: \m {16}
\I How many noise standard deviation tried: \m {7}
\I Solved by Python CVXPY
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Repetition times}
{
\I Number of channels ...
\I of each LS case: \m {64 \D 48}
\I of each OMP case: \m {64 \D 24}
\I of each Lasso case: \m {64 \D 2}
\I of each DS case: \m {64 \D 1}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Assorted, Efficiency, \m {N_H=12}}
{
\blank [big]
\externalfigure [assorted-small-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Assorted, Efficiency, \m {N_H=18}}
{
\blank [big]
\externalfigure [assorted-medium-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Assorted, Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Assorted, Time Taken, \m {N_H=18}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {DS, Efficiency, \m {N_H=12}}
{
\blank [big]
\externalfigure [ddss-small-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {DS, Efficiency, \m {N_H=18}}
{
\blank [big]
\externalfigure [ddss-medium-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {DS, Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [ddss-big-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {DS, Time Taken, \m {N_H=18}}
{
\blank [big]
\externalfigure [ddss-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {OMP, Efficiency, \m {N_H=12}}
{
\blank [big]
\externalfigure [oommpp-small-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {OMP, Efficiency, \m {N_H=18}}
{
\blank [big]
\externalfigure [oommpp-medium-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {OMP, Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [oommpp-big-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {OMP, Time Taken, \m {N_H=18}}
{
\blank [big]
\externalfigure [oommpp-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins with a narrow margin for smaller \m {\s}, but it gets poorer for larger \m {\s}.

\I \m {\eta _{\Ss {th}}} is in correct order of magnitude for larger \m {\s}, but an overestimation for smaller \m {\s}.

\I The performance of DS seems not to be sensitive to \m {\g _{\Ss {DS}}}.

\I DS has very high complexity compared to OMP, and similar complexity with Lasso.

\I The requirement that \m {N_H \gg N_R \gg N_Y} is demanding, and \m {2N_H^2} grows fast.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (1/2)}
{
\I The number of Newton steps in the course of optimization is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.

\I Every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.

\I This gives overall complexity to be \m {\MC {O} \SB {N_H^6}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (2/2)}
{
\I Alternatively, Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.

\I Since DS and Lasso have similar form, we expect DS has similar complexity.

\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
}

### 2020-06-09 presentation/5_conclusion.tex
Update presentation

\Frame {Conclusion}
{
\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by exploiting its sparsity, and employing Dantzig Selector (DS).

\I We modified DS for present setting, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.

\I We have a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.

\I We adopt linear programming to reduce complexity.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Is it possible to resort to less precision to reduce complexity, but retaining the performance?

\I Run for bigger values of \m {N_H}, \m {N_Y} and repeat for enough times to observe a definite result.

\I I want to know why DS is not as good as expected, and to provide discussion, before closing the case.

\I The proof section need some rewriting, but it is not big deal.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References}
{
{\tfx
\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.

@@

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.

\I B Efron and T Hastie, \Quote {Least angle regression}, \Quote {The Annals of statistics}, 32(2), 2004.

\I J Lee, G-T Lee, and H Yong, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
}
}

>>>>

\Frame {Conclusion}
{
\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by modifying Dantzig Selector (DS), exploiting the sparsity inherent in the problem.

\I We argue for its validity, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.

\I We propose a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.

\I We convert the problem into a linear program to reduce complexity, and run a two-stage version to estimate the position of components.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Is it possible to reduce complexity, while retaining the performance?

\I Is the trend the same for bigger values of \m {N_H}?

\I Why DS is not as good as expected, and is there any mistakes in the proof of error bound?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010

\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.

@@

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (2/2)}
{
{\tfx
\I E J Candès and T Tao, \Quote {Decoding by Linear Programming}, \It {IEEE Transactions on Information Theory}, 51(12), 2005

\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when p is much larger than n}, \It {The Annals of Statistics}, 35(6), 2007

\I J Lee, G-T Lee, and H Yong, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.

\I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 53(12), 2007.
}
}
